---
title: "limma_race"
output: html_document
date: "2022-10-24"
---


######################## Work Space Setup
```{r Required Packages}

library('viridis')
library('ggstatsplot')
library('RColorBrewer')
library('metafor')
library('dplyr')
library('biomaRt')
library('ggrepel')
library('ggbeeswarm')
library('patchwork')
library("gprofiler2")
library("biomaRt")
library("reshape2")
library("gghighlight")
library("rrvgo")
library("ggVennDiagram")
library("wesanderson")
library("parallel")
library("magrittr")
library("foreach")
library("doParallel")
library("org.Hs.eg.db")

```

```{r Plot Themes}

My_Theme = theme(
  axis.title.x = element_text(size = 16),
  axis.text.y = element_text(size = 14),
  axis.text.x = element_text(size = 14),
  axis.title.y = element_text(size = 16))

```



######################## Concordance Analysis
```{r Concordance Plot - Cross-Cohort Signature of Race}

#### DEG across Race
DEG_PPM_race <- data.frame(DE[[1]]) #%>% filter(hgnc_symbol != c('')) 
DEG_NIMH_race <- data.frame(DE[[2]]) #%>% filter(hgnc_symbol != c('')) 

  race_NIMH <- DEG_NIMH_race %>% dplyr::rename_at("t",~"NIMH_t")
  race_PPM <- DEG_PPM_race %>% dplyr::rename_at("t",~"PPM_t")
    # Join the tables together
    cmc_race_cohort <- dplyr::inner_join(race_NIMH, 
                                         race_PPM, by = "ensembl_gene_id")
  # Run the correlation test
  corr_cmc_race_cohort <- cor.test(cmc_race_cohort$NIMH_t, 
                                   cmc_race_cohort$PPM_t, method = "spearman")
# See the results
corr_cmc_race_cohort

cohort_race_reg <- lm(NIMH_t ~ PPM_t, data = cmc_race_cohort)
summary(cohort_race_reg)

corr_race_cohort <- ggplot(cmc_race_cohort , aes(x = NIMH_t, y=PPM_t)) + 
    theme_bw() +
    geom_vline(xintercept=0, col="black", linetype = "longdash") +
        geom_hline(yintercept=0, col="black", linetype = "longdash") +
        ylim(-5,5) +
            xlim(-8,8) + 
            geom_abline(slope = 1, col ='red') +
        xlab('NIMH-HBCC test-statistic') +
        ylab('MSSM-Penn-Pitt test-statistic') +
          ggpointdensity::geom_pointdensity(adjust = 1, size = 0.5 , alpha = 3) +
          scale_color_viridis(option = 'cividis') + 
        geom_density_2d(linewidth = 0.25, colour = "black") +
        geom_smooth(method='lm', formula= y~x, color = "orange") +
      labs(colour = "Density") +
    scale_fill_continuous(breaks = c(500, 2000)) +  
    guides(colour = guide_colourbar(direction = "vertical")) +
  geom_abline(slope = 1) +
  ggpubr::stat_cor(method = "spearman", color = 'red', size = 5) + My_Theme +
theme(legend.position = c(0.94, 0.25)) + 
guides(shape = guide_legend(override.aes = list(size = 0.5)))

corr_race_cohort
     
```



######################## Mega - Analysis
```{r Parse the Mega-Analysis Effect Size}

DE_mega_race = DE_mega
sig_race = DE_mega %>% dplyr::filter(abs(logFC) > 0.25 & adj.P.Val < 0.05)

```

```{r Volcano of Mega-Analysis}

volcano_mega_race <- make_volcano_plot_race(DE_mega_race, x_lim = c(-5, 5), y_lim = c(0, 25))
volcano_mega_race

```

```{r Volcano of Mega-Analysis CTRA only}

# Filter only sig CTRA genes
ctra_genes_race <- DE_mega_race %>% dplyr::filter(DE_mega_race$hgnc_symbol %in% CTRA)

# Plot the Volcano
volcano_mega_race_ctra <- make_volcano_plot_CTRA(ctra_genes_race, x_lim = c(-1, 1), y_lim = c(0, 20))
volcano_mega_race_ctra 

```



######################## Meta - Analysis *requires cohort-specific signatures*
```{r Example of metafor on one gene -- conceptual understanding step}

# have to do the analysis separately for each gene across either cohort
# remember you can only compare genes that are in BOTH cohorts

# yi is the effect sizes (in this case it is the LFC); vi are the variances
# sei is the standard error (the measure of change by the t stat) = LFC/t-stat

meta_1 <- metafor::rma(yi = c(DE$`MSSM-Penn-Pitt`$logFC[1],DE$`NIMH-HBCC`$logFC[1]),
                       sei = c(DE$`MSSM-Penn-Pitt`$logFC[1]/DE$`MSSM-Penn-Pitt`$t[1], 
                               DE$`NIMH-HBCC`$logFC[1]/DE$`NIMH-HBCC`$t[1]), 
                       method="FE", weighted=TRUE, data=DE) 

forest(meta_1)
summary(meta_1)

```

```{r Create the DE frames for the meta-analysis}

# Clean up the data frames and add columns denoting the Cohort + select the columns of interest
DEG_NIMH_race$Cohort <- "NIMH"
meta_NIMH <- DEG_NIMH_race %>% 
  dplyr::rename(logFC_NIMH = logFC, t_NIMH = t , hgnc_symbol_NIMH = hgnc_symbol) %>%
  dplyr::select('logFC_NIMH','t_NIMH', 'hgnc_symbol_NIMH', 
                'description', 'gene_id', 'Cohort')

DEG_PPM_race$Cohort <- "PPM"
meta_PPM <- DEG_PPM_race %>% 
  dplyr::rename('logFC_PPM' = 'logFC', 't_PPM' = 't', 
                'hgnc_symbol_PPM' = 'hgnc_symbol') %>% 
  dplyr::select('logFC_PPM','t_PPM', 
                'hgnc_symbol_PPM', 'gene_id', 'Cohort')

# Turn the dataframes into a list
meta_mega <- list(meta_NIMH, meta_PPM)
names(meta_mega) <- c("NIMH-HBCC", "MSSM-Penn-Pitt")
genes <- meta_mega$`NIMH-HBCC`$gene_id #%>% unique()

```

```{r Assess the Meta-analysis Effect Size}

gene_names_race_meta <- cmc_meta_analysis(meta_mega, genes)

colnames(gene_names_race_meta)
colnames(DE_mega)

```

```{r Meta-anlaysis volcano plot}

# Run the function
volcano_meta_race <- make_volcano_plot_race(gene_names_race_meta, x_lim = c(-2, 2), y_lim = c(0, 6))
volcano_meta_race

# This is a data frame of the top 50 up and downregulated genes
meta_race_genes <- as.data.frame(volcano_meta_race$plot_env$top_50_genes)

#ggsave("volcano_meta_race.png", path = "/Users/shuaybsimmons/Desktop/School/UofT MSc Medical Science/Research/Thesis Research/Plots/Race")

```



######################## Residual Count Plots Analysis
```{r Create the vectors of race in NIMH & PPM}

# This is a vector of Black samples in NIMH-HBCC
black_people_NIMH <- METADATA %>% dplyr::filter(Ethnicity == "AA" & Cohort == "NIMH-HBCC")
  black_samples_NIMH <- c(black_people_NIMH$SampleID)
# This is a vector of white samples in NIMH-HBCC
white_people_NIMH <- METADATA %>% dplyr::filter(Ethnicity == "C" & Cohort == "NIMH-HBCC")
  white_samples_NIMH <- c(white_people_NIMH$SampleID)
  
# This is a vector of Black samples in NIMH-HBCC
black_people_PPM <- METADATA %>% dplyr::filter(Ethnicity == "AA" & Cohort == "MSSM-Penn-Pitt")
  black_samples_PPM <- c(black_people_PPM$SampleID)
# This is a vector of white samples in NIMH-HBCC
white_people_PPM <- METADATA %>% dplyr::filter(Ethnicity == "C" & Cohort == "MSSM-Penn-Pitt")
  white_samples_PPM <- c(white_people_PPM$SampleID)

```

```{r Create and clean the residual dfs}

# Clean the data frame for NIMH-HBCC
residuals_race_NIMH_raw = as.data.frame(resid.add$Ethnicity$`NIMH-HBCC`)
residuals_race_NIMH_cleaned <- clean_dataframe_nimh(residuals_race_NIMH_raw)
colnames(residuals_race_NIMH_cleaned)

# Clean the data frame for MSSM-Penn-Pitt
residuals_race_PPM_raw = as.data.frame(resid.add$Ethnicity$`MSSM-Penn-Pitt`)
residuals_race_PPM_cleaned <- clean_dataframe_ppm(residuals_race_PPM_raw)
colnames(residuals_race_PPM_cleaned)

```

```{r Merge the frames and select genes to visualize}

# Rbind the frames together
all_residuals_race = rbind(residuals_race_NIMH_cleaned, residuals_race_PPM_cleaned) 
colnames(all_residuals_race)

# left join the metadata to the residual counts by cohort and SampleID
residuals_met_sheet <- dplyr::left_join(METADATA, all_residuals_race, 
                                 by = c("SampleID" = "SampleID", 
                                        "Cohort" = "Cohort")) %>%
mutate(Ethnicity = dplyr::recode(Ethnicity, AA = "Black", C = "White"))

# Select the genes we're interested in seeing --  make an annotation function!!
highlighted_genes = c("ENSG00000276070","ENSG00000259823",
                      "ENSG00000151655","ENSG00000239961")
plot_all = residuals_met_sheet %>% 
  dplyr::filter(Gene_ID %in% highlighted_genes) %>%
  dplyr::mutate(Gene_ID = dplyr::recode(Gene_ID, 
                                        ENSG00000276070 = "CCL4L2", 
                                        ENSG00000259823 = "LYPD8",
                                        ENSG00000151655 = "ITIH2",
                                        ENSG00000239961 = "LILRA4"))
  
```

```{r Plot residuals of race (of select genes) across cohort}

genes_res_race <- plot_gene_residuals_by_race(plot_all, My_Theme, c("#D3D3D3", "#4F4F4F"))
genes_res_race

```



######################## Genetic Ancestry Vectors vs Race Plots Analysis
```{r Plot ancestry (EV.1) versus residual counts}

# Create by factor
plot_all$Ethnicity <- as.factor(plot_all$Ethnicity)
plot_all$Ethnicity <- relevel(plot_all$Ethnicity, ref = "White")

ancestry_vs_race <- ggplot(plot_all, 
                           aes(x = EV.1, y = Res_counts, fill = Ethnicity)) +
  # EV.1 and ethnicity
  geom_point(aes(color = Ethnicity), alpha = 0.5) +
    # Residual Counts and ethnicity
  #  geom_boxplot(aes(fill = Ethnicity), color = "#4F4F4F", width = 0.3) +
    xlab('Genetic Ancestry Vector') + ylab('Expression Residuals') +  facet_grid(Cohort ~ Gene_ID, scales = "free_y") +
  theme_bw() + theme(legend.position = "none") + 
  scale_color_manual(values = c("#4F4F4F" = "#4F4F4F", "White" = "#D3D3D3")) +
scale_fill_manual(values = c("#4F4F4F" = "#4F4F4F", "White" = "#D3D3D3")) + 
      theme(strip.text.x = element_text(size = 11.5, color = "Black"),
          strip.text.y = element_text(size = 11, color = "Black"),
          axis.title.x = element_text(size = 11),
          axis.text.y = element_text(size = 11),
          axis.text.x = element_text(size = 12),
          axis.title.y = element_text(size = 11)) 

ancestry_vs_race

```



######################## Gene Ontology Enrichment Analysis 
```{r directional mega-analysis}

# Run the directional ontology analysis
mega_ontology_race_list <- directional_GO_analysis(DE_mega_race, LFC_threshold = 0.25)
mega_ontology_race_list

# Create the data frame of terms from the list
top_mega_race_UP <- as.data.frame(mega_ontology_race_list$UP)
top_mega_race_DOWN <- as.data.frame(mega_ontology_race_list$DOWN)

```

```{r hierarchal mega-analysis}

# Run the hierarchical ontology analysis
hierarchy_UP <- runGOAnalysis(top_mega_race_UP)
hierarchy_DOWN <- runGOAnalysis(top_mega_race_DOWN)

```



######################## Ontology Concordance Analysis [Mega-Analysis Only]
```{r Immune System Process Genes}

# Clean the data frame up
immune_system_process$Symbol = toupper(immune_system_process$Symbol)

race_NIMH_immune <- DEG_NIMH_race %>% rename_at("t",~"NIMH_t") %>% filter(hgnc_symbol %in% immune_system_process$Symbol)
race_PPM_immune <- DEG_PPM_race %>% rename_at("t",~"PPM_t") %>% filter(hgnc_symbol %in% immune_system_process$Symbol)

cmc_race_cohort_immune <- inner_join(race_NIMH_immune,race_PPM_immune, by = "ensembl_gene_id")

corr_race_cohort_immune <- ggplot(cmc_race_cohort, aes(x = NIMH_t, y=PPM_t)) + 
   geom_point(size=1.5, color="red") + theme_classic() +
   geom_vline(xintercept=0, col="black", linetype = "longdash") +
   geom_hline(yintercept=0, col="black", linetype = "longdash") +
        ylim(-5,5) +
            xlim(-8,8) + 
        xlab('NIMH-HBCC test-statistic') +
        ylab('MSSM-Penn-Pitt test-statistic') +
  ggtitle('Immune System Process') + 
guides(colour = guide_colourbar(direction = "vertical")) +
My_Theme 

named_corr_race_cohort_immune <- corr_race_cohort_immune + geom_text_repel(data=cmc_race_cohort_immune,
                  aes(label=hgnc_symbol.x), colour = "black") + 
    stat_cor(method = "spearman", color = 'red', size = 5, aes(label = ..r.label..))

named_corr_race_cohort_immune_highlight <- named_corr_race_cohort_immune +
        geom_smooth(method='lm', formula= y~x, color = "orange", linetype = "dashed", se = FALSE) +
  gghighlight::gghighlight(hgnc_symbol.x %in% immune_system_process$Symbol) 

named_corr_race_cohort_immune_highlight 

```

```{r Response to stimulus}

stimulus_genes$Symbol = toupper(stimulus_genes$Symbol)

race_NIMH_stimulus <- DEG_NIMH_race %>% rename_at("t",~"NIMH_t") %>% filter(hgnc_symbol %in% stimulus_genes$Symbol)
race_PPM_stimulus <- DEG_PPM_race %>% rename_at("t",~"PPM_t") %>% filter(hgnc_symbol %in% stimulus_genes$Symbol)


cmc_race_cohort_stimulus <- inner_join(race_NIMH_stimulus, race_PPM_stimulus, by = "ensembl_gene_id")

corr_race_cohort_stimulus <- ggplot(cmc_race_cohort, aes(x = NIMH_t, y=PPM_t)) + 
   geom_point(size=1.5, color="red") + theme_classic() +
   geom_vline(xintercept=0, col="black", linetype = "longdash") +
   geom_hline(yintercept=0, col="black", linetype = "longdash") +
        ylim(-5,5) +
            xlim(-8,8) + 
        xlab('NIMH-HBCC test-statistic') +
        ylab('MSSM-Penn-Pitt test-statistic') +
  ggtitle('Response to stimulus') + 
guides(colour = guide_colourbar(direction = "vertical")) +
My_Theme 

named_corr_race_cohort_stimulus <- corr_race_cohort_stimulus + 
  geom_text_repel(data=cmc_race_cohort_stimulus,
                  aes(label=hgnc_symbol.x), colour = "black")

named_corr_race_cohort_stimulus_highlight <- named_corr_race_cohort_stimulus +
        geom_smooth(method='lm', formula= y~x, color = "orange", linetype = "dashed", se = FALSE) +
  stat_cor(method = "spearman", color = 'red', size = 5, aes(label = ..r.label..)) +
  gghighlight::gghighlight(hgnc_symbol.x %in% stimulus_genes$Symbol) 


named_corr_race_cohort_stimulus_highlight

```



######################## Overlap between reported race and the CTRA
```{r TwoWayVenn}

race = DE_mega_race %>% 
  dplyr::filter(abs(logFC) > 0.25 & adj.P.Val < 0.05) %>% 
dplyr::filter(!is.na(hgnc_symbol) & hgnc_symbol != "")
race = c(race$hgnc_symbol)


CTRA <- c("IL1A", "IL1B", "IL6", "IL8", "TNF", "PTGS1", 
                     "PTGS2", "FOS", "FOSB", "FOSL1", "FOSL2", "JUN", 
                     "JUNB", "JUND", "NFKB1", "NFKB2", "REL", "RELA", 
                     "RELB", "GBP1", "IFI16", "IFI27", "IFI27L2", "IFI27L2", "IFI30", "IFI35", 
                "IFI44", "IFI44L", "IFI6", "IFIH1", "IFIT1","IFIT2", "IFIT3","IFIT5", 
                "IFIT1L", "IFITM1–3", "IFITM2", "IFITM3", "IFITM4P", "IFITM5", "IFNB1", 
                "IRF2", "IRF7", "IRF8", "MX1", "MX2", "OAS1", "OAS2", "OAS3", "OASL", "IGJ", "IGLL1", 
                "IGLL3")  

yo <- intersect(CTRA, race) 
  
# Merge the vectors of genes into a list
CTRA_race = list(A = race,
                 B = CTRA)

category_names <- c("Gene Expression Siganature of Race",
                    "Controlled Transcriptional Response to Adversity (CTRA)")


twoway_venn <- draw_venn(CTRA_race, category_names, 2)
twoway_venn

```

```{r Shared_CTRA_Race}

# Upregulated
race_upregulated = DE_mega_race %>% 
  dplyr::filter(logFC > 0.25 & adj.P.Val < 0.05) %>% 
    dplyr::filter(!is.na(hgnc_symbol) & hgnc_symbol != "")
  race_upregulated_genes = c(race_upregulated$hgnc_symbol)
range(race_upregulated$logFC, na.rm = FALSE)

# Downregulated
race_downregulated = DE_mega_race %>% 
  dplyr::filter(logFC < -0.25 & adj.P.Val < 0.05) %>% 
    dplyr::filter(!is.na(hgnc_symbol) & hgnc_symbol != "")
  race_downregulated_genes = c(race_downregulated$hgnc_symbol)
range(race_downregulated$logFC, na.rm = FALSE)

proinflammation <- c("IL1A", "IL1B", "IL6", "IL8", "TNF", "PTGS1", 
                     "PTGS2", "FOS", "FOSB", "FOSL1", "FOSL2", "JUN", 
                     "JUNB", "JUND", "NFKB1", "NFKB2", "REL", "RELA", 
                     "RELB")    
  
interferon <- c("GBP1", "IFI16", "IFI27", "IFI27L2", "IFI27L2", "IFI30", "IFI35", 
                "IFI44", "IFI44L", "IFI6", "IFIH1", "IFIT1","IFIT2", "IFIT3","IFIT5", 
                "IFIT1L", "IFITM1–3", "IFITM2", "IFITM3", "IFITM4P", "IFITM5", "IFNB1", 
                "IRF2", "IRF7", "IRF8", "MX1", "MX2", "OAS1", "OAS2", "OAS3", "OASL", "IGJ", "IGLL1", 
                "IGLL3")  

# Merge the vectors of genes into a list
genes_cmc = list(A = race_upregulated_genes,
                 B = race_downregulated_genes,
                 C = proinflammation,
                 D = interferon)

category_names <- c("Up in Black",
                    "Up in White",
                    "Pro-inflammatory (CTRA up)",
                    "Interferon (CTRA down)")

fourway_venn <- draw_venn(genes_cmc, category_names, 4)
fourway_venn

```

```{r Hypergeometric_Testing}

# Step 1: Calculate the number of overlapping elements
overlap_count <- length(intersect(CTRA, DE_mega_race$hgnc_symbol))

# Step 2: Calculate the total number of elements in each vector
total_ctra <- length(CTRA)
total_hgnc_symbol <- length(DE_mega_race$hgnc_symbol)

# Step 3: Calculate the p-value using the hypergeometric test
p_value <- phyper(overlap_count - 1, total_ctra, total_hgnc_symbol, length(unique(DE_mega_race$hgnc_symbol)))

# Step 4: Interpret the p-value and print the result along with the p-value
if (p_value < 0.05) {
  print("The overlap between the two vectors is statistically significant.")
} else {
  print("The overlap between the two vectors is not statistically significant.")
}
cat("p-value:", p_value, "\n")

```

######################## Pretin Coding genes across cohort -- this is so weird!
```{r NIMH-HBCC}

biotype_counts_NIMH <- as.data.frame(table(DEG_NIMH_race$gene_biotype))

biotype_counts_NIMH$Cohort<- "NIMH-HBCC"

# Keep only biotypes with at least 100 genes -- or else it gets messy
#biotype_counts_NIMH <- biotype_counts_NIMH[biotype_counts_NIMH$Freq >= 100,]
biotype_counts_NIMH = dplyr::rename(biotype_counts_NIMH, Gene_Biotype = Var1)
biotype_counts_NIMH = dplyr::rename(biotype_counts_NIMH, Gene_Number = Freq)
unique(biotype_counts_NIMH$Gene_Biotype)

# Recode the values for better plot graphics  
biotype_counts_NIMH = biotype_counts_NIMH %>% mutate(Gene_Biotype = recode(Gene_Biotype,
                               lncRNA = "long-non coding RNA",
                               processed_pseudogene = "processed pseudogene",
                               protein_coding = "protein coding",
                               TEC = "TBD",
                               transcribed_processed_pseudogene = "transcribed processed pseudogene",
                               transcribed_unprocessed_pseudogene = "transcribed unproc pseudogene",
                               unprocessed_pseudogene = "unprocessed pseudogene"))
biotype_counts_NIMH = biotype_counts_NIMH %>% dplyr::arrange(desc(Gene_Number))

```

```{r Penn-Pitt-MSSM}

biotype_counts_PPM <- as.data.frame(table(DEG_PPM_race$gene_biotype))
biotype_counts_PPM$Cohort<- "Penn-Pitt-MSSM"

#biotype_counts_PPM <- biotype_counts_PPM[biotype_counts_PPM$Freq >= 100,]
biotype_counts_PPM = dplyr::rename(biotype_counts_PPM, Gene_Biotype = Var1)
biotype_counts_PPM = dplyr::rename(biotype_counts_PPM, Gene_Number = Freq)
unique(biotype_counts_PPM$Gene_Biotype)

# Recode the values for better plot graphics  
biotype_counts_PPM = biotype_counts_PPM %>% dplyr::mutate(Gene_Biotype = recode(Gene_Biotype,
                               lncRNA = "long-non coding RNA",
                               processed_pseudogene = "processed pseudogene",
                               protein_coding = "protein coding",
                               TEC = "TBD",
                               transcribed_processed_pseudogene = "transcribed processed pseudogene",
                               transcribed_unprocessed_pseudogene = "transcribed unproc pseudogene",
                               unprocessed_pseudogene = "unprocessed pseudogene"))
biotype_counts_PPM = biotype_counts_PPM %>% dplyr::arrange(desc(Gene_Number))

```

```{r plotting biotype counts}

biotype_counts = rbind(biotype_counts_NIMH, biotype_counts_PPM)

race_genes_mega_coding <- ggplot(data = biotype_counts) + 
   geom_col(aes(x=reorder(Gene_Biotype, + Gene_Number), y=Gene_Number, fill = Cohort), 
            stat = "identity", position = "dodge") + theme_classic() +
    theme(legend.position = "none") + theme(axis.text.x = element_text(angle = 90)) + 
  scale_fill_manual(values = c("#9BC53D", "#FFBF00"))+
  xlab("Gene Biotype") + ylab("Number of genes") 

      
race_genes_mega_coding

```



####################### Save the Plots
```{r Save the Plots}
#ggsave("corr_race_cohort.png", width = 8, height = 7, path = "/Users/shuaybsimmons/Desktop/School/UofT MSc Medical Science/Research/Thesis Research/Plots/Race")

#ggsave("volcano_mega_race.png", path = "/Users/shuaybsimmons/Desktop/School/UofT MSc Medical Science/Research/Thesis Research/Plots/Race/Mega-Analysis")

# ggsave("genes_res_race.png", width = 7, height = 7, path = "/Users/shuaybsimmons/Desktop/School/UofT MSc Medical Science/Research/Thesis Research/Plots/Race/Mega-Analysis/")

#ggsave("volcano_mega_race_ctra.png", width = 7, height = 7, path = "/Users/shuaybsimmons/Desktop/School/UofT MSc Medical Science/Research/Thesis Research/Plots/Race/Mega-Analysis/")

#ggsave("ancestry_vs_race.png", width = 7, height = 7, path = "/Users/shuaybsimmons/Desktop/School/UofT MSc Medical Science/Research/Thesis Research/Plots/Race/Mega-Analysis/")

#ggsave("mega_ontology_race_list.png", width = 9, height = 7, path = "/Users/shuaybsimmons/Desktop/School/UofT MSc Medical Science/Research/Thesis Research/Plots/Race/Mega-Analysis/")

#ggsave("named_corr_race_cohort_immune_highlight.png",width = 8, height = 7, path = "/Users/shuaybsimmons/Desktop/School/UofT MSc Medical Science/Research/Thesis Research/Plots/Race")

#ggsave("named_corr_race_cohort_stimulus_highlight.png", width = 8, height = 7, path = "/Users/shuaybsimmons/Desktop/School/UofT MSc Medical Science/Research/Thesis Research/Plots/Race")

# ggsave("fourway_venn.png", width = 6, height = 7, path = "/Users/shuaybsimmons/Desktop/School/UofT MSc Medical Science/Research/Thesis Research/Plots/Race/Mega-Analysis/")

```